Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-30 main-disk-model.tex
minor
more written on events

    An event can happen on finish or start of a task execution or an io action (file read or write).
    Each event has several parameters:
    \begin{itemize}
        \item Event type: OnTaskStart, OnTaskFinish, OnIoStart, OnIoFinish
        \item The action associated with the event: the task to be executed or an edge whose file needs to be read or written
        \item The processor id on which the action should take place
        \item Expected and actual time of firing.
        \item A set of predecessor events. The event is called ready if all its predecessors have been finished.
        \item A set of successor events to keep track of.
    \end{itemize}

@@

    When a processor is chosen, the scheduler inserts new events into the queue:
    \begin{itemize}
        \item For the task, OnTaskStart and OnTaskFinish events with the estimated trigger times, the OnTaskFinish event being dependent on the OnTaskStart event.
        \item For each io operation necessary for the execution: OnIoStart event of the corresponding type and on corresponding processor
        \item It connects all the event with predecessor-successor relations.
    \end{itemize}
    THe scheduler also updates the ready times of the processors and updates the new currently last events there.

    \paragraph{On Task Start}
    When a task start event is triggered, it determines the deviation of the runtime of the task.
    It applies the deviation function on its estimated runtime (estimated finish minus estimated start time).
    It then adds this deviated runtime to its actual start time and receives an updated actual finish time.
    With this time, it updates the OnTaskFinish event of this task.

>>>>

    An event can happen on finish or start of a task execution or an io action (file read or write).
    Each event has several parameters:
    \begin{itemize}
        \item Event type: OnTaskStart, OnTaskFinish, OnIoStart, OnIoFinish
        \item The action associated with the event: the task to be executed or an edge whose file needs to be read or written
        \item The processor id on which the action should take place
        \item Expected and actual time of firing.
        \item A set of predecessor events. The event is called ready if all its predecessors have been finished.
        \item A set of successor events to keep track of.
        \item For a write event, a boolean if this file should be removed from memory after being written.
    \end{itemize}

@@

    When a processor is chosen, the scheduler inserts new events into the queue:
    \begin{itemize}
        \item For the task, OnTaskStart and OnTaskFinish events with the estimated trigger times, the OnTaskFinish event being dependent on the OnTaskStart event.
        \item For each io operation necessary for the execution: OnIoStart event of the corresponding type and on corresponding processor
        \item It connects all the event with predecessor-successor relations.
    \end{itemize}
    The scheduler also updates the ready times of the processors and updates the new currently last events there.

    \paragraph{On Task Start}
    When a task start event is triggered, it first determines if it can start.
    If some predecessor tasks have not yet finished (the predecessor set is not empty), then the actual time of this event
    is set to the maximum of the estimated end times of predecessor events and this event is reinserted in the queue
    with this new time.

    If the task can start, the scheduler determines the deviation of the runtime of the task.
    It applies the deviation function on its estimated runtime (estimated finish minus estimated start time).
    It then adds this deviated runtime to its actual start time and receives an updated actual finish time.
    With this time, it updates the OnTaskFinish event of this task.

    \paragraph{OnIoFinish}
    When the io operation finishes, it removes itself from the predecessor sets of all its successor events.
    It also sets their actual time to its own actual finish time.

    \paragraph{OnIOStart}
    When the IO operation starts, it updates the corresponding IoFinish event

    After being triggered and completed, each event is deleted from the queue.

--------------------------------------
